Chemical tagging can work: \\ Identification of stellar phase-space structures \\ purely by chemical-abundance similarity

### 2016-01-19 papers/clusters.tex
Typos and washing Hogg's mouth with soap

% text shit
\newcommand{\acronym}[1]{{\small{#1}}}
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\sdssiii}{\project{\acronym{SDSS-III}}}
\newcommand{\apogee}{\project{\acronym{APOGEE}}}
\newcommand{\aspcap}{\project{\acronym{ASPCAP}}}
\newcommand{\gaiaeso}{\project{Gaia--\acronym{ESO}}}
\newcommand{\galah}{\project{\acronym{GALAH}}}
\newcommand{\thecannon}{\project{The~Cannon}}
\newcommand{\foreign}[1]{\textsl{#1}}
\newcommand{\etal}{\foreign{et~al.}}
\newcommand{\documentname}{\textsl{Article}}
\newcommand{\sectionname}{Section}

% math shit
\newcommand{\teff}{T_{\mathrm{eff}}}
\newcommand{\logg}{\log g}

% figure shit
\newlength{\figwidth}\setlength{\figwidth}{0.3\textwidth}
\newcommand{\insanefigure}[1]{%
\includegraphics[width=\figwidth]{./figs/#1_MgFe.png}%
\includegraphics[width=\figwidth]{./figs/#1_MgK.png}%
\includegraphics[width=\figwidth]{./figs/#1_AlMg.png}\\
\includegraphics[width=\figwidth]{./figs/#1_NaO.png}%
\includegraphics[width=\figwidth]{./figs/#1_CN.png}%
\includegraphics[width=\figwidth]{./figs/#1_SAl.png}\\
\includegraphics[width=2\figwidth]{./figs/#1_gal.png}%
\includegraphics[width=\figwidth]{./figs/#1_HR.png}\\
\includegraphics[width=2\figwidth]{./figs/#1_vlon.png}}

% results shit
\newcommand{\totalnumber}{98462}

@@

\title{Chemical tagging can work: \\
       Identification of stellar phase-space structures \\
       purely by chemical-abundance similarity}
\author{David~W.~Hogg\altaffilmark{1,2,3,4},
        Andrew~R.~Casey\altaffilmark{5},
        Melissa~Ness\altaffilmark{4}, % typeset as per MKN-DWH email conversation 2016-01-18
        Hans-Walter~Rix\altaffilmark{4},
    and~Daniel~Foreman-Mackey\altaffilmark{6,7}}
\altaffiltext{1}{Simons Center for Data Analysis, 160 Fifth Avenue, 7th Floor, New York, NY 10010, USA}
\altaffiltext{2}{Center for Cosmology and Particle Physics, Department of Phyics,
  New York University, 4 Washington Pl., room 424, New York, NY, 10003, USA}
\altaffiltext{3}{Center for Data Science, New York University, 726 Broadway, 7th Floor, New York, NY 10003, USA}
\altaffiltext{4}{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117 Heidelberg, Germany}
\altaffiltext{5}{Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3~0HA, UK}
\altaffiltext{6}{Sagan Fellow}
\altaffiltext{7}{Department of Astronomy, University of Washington, Box 351580, Seattle, WA 98195-1580}
\email{david.hogg@nyu.edu}

>>>>

% text
\newcommand{\acronym}[1]{{\small{#1}}}
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\sdssiii}{\project{\acronym{SDSS-III}}}
\newcommand{\apogee}{\project{\acronym{APOGEE}}}
\newcommand{\aspcap}{\project{\acronym{ASPCAP}}}
\newcommand{\gaiaeso}{\project{Gaia--\acronym{ESO}}}
\newcommand{\galah}{\project{\acronym{GALAH}}}
\newcommand{\thecannon}{\project{The~Cannon}}
\newcommand{\foreign}[1]{\textsl{#1}}
\newcommand{\etal}{\foreign{et~al.}}
\newcommand{\documentname}{\textsl{Article}}
\newcommand{\sectionname}{Section}

% math
\newcommand{\teff}{T_{\mathrm{eff}}}
\newcommand{\logg}{\log g}

% figure 
\newlength{\figwidth}\setlength{\figwidth}{0.3\textwidth}
\newcommand{\insanefigure}[1]{%
\includegraphics[width=\figwidth]{./figs/#1_MgFe.png}%
\includegraphics[width=\figwidth]{./figs/#1_MgK.png}%
\includegraphics[width=\figwidth]{./figs/#1_AlMg.png}\\
\includegraphics[width=\figwidth]{./figs/#1_NaO.png}%
\includegraphics[width=\figwidth]{./figs/#1_CN.png}%
\includegraphics[width=\figwidth]{./figs/#1_SAl.png}\\
\includegraphics[width=2\figwidth]{./figs/#1_gal.png}%
\includegraphics[width=\figwidth]{./figs/#1_HR.png}\\
\includegraphics[width=2\figwidth]{./figs/#1_vlon.png}}

% results
\newcommand{\totalnumber}{98462}

@@

\title{Chemical tagging can work: \\
       Identification of stellar phase-space structures \\
       purely by chemical-abundance similarity}
\author{David~W.~Hogg\altaffilmark{1,2,3,4},
        Andrew~R.~Casey\altaffilmark{5},
        Melissa~Ness\altaffilmark{4},
        Hans-Walter~Rix\altaffilmark{4},
    and~Daniel~Foreman-Mackey\altaffilmark{6,7}}
\altaffiltext{1}{Simons Center for Data Analysis, 160 Fifth Avenue, 7th Floor, New York, NY 10010, USA}
\altaffiltext{2}{Center for Cosmology and Particle Physics, Department of Physics,
  New York University, 4 Washington Pl., room 424, New York, NY, 10003, USA}
\altaffiltext{3}{Center for Data Science, New York University, 726 Broadway, 7th Floor, New York, NY 10003, USA}
\altaffiltext{4}{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117 Heidelberg, Germany}
\altaffiltext{5}{Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3~0HA, UK}
\altaffiltext{6}{Sagan Fellow}
\altaffiltext{7}{Department of Astronomy, University of Washington, Box 351580, Seattle, WA 98195-1580}
\email{david.hogg@nyu.edu}
